---
title: "Shifting Sands of Canada"
author: "Analyzing Changing Interprovincial Migration Trends"
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    latex_engine: xelatex
  html_document:
    df_print: paged
  word_document: default
header-includes: \usepackage{setspace}
always_allow_html: yes
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

------------------------------------------------------------------------

# TEAM MEMBERS: Group SAAS

## *Huynh Hiep Tran (Alex)* - T00728369

## *Shivani Tyagi* - T00727866

## *Sayantika Saha* - T00731231

## *Mohd Asaf Shaikh* -- T00728877

------------------------------------------------------------------------

# TABLE OF CONTENT

1.  [Project Objective](#section-one)
2.  [About Dataset](#section-two)
3.  [Data Preprocessing](#section-three)
4.  [Trend Analysis](#section-four)
5.  [Hypothesis Testing](#section-five)
6.  [Conclusion](#section-six)
7.  [References](#section-seven)

------------------------------------------------------------------------

# PROJECT OBJECTIVE {#section-one}

This project focuses on investigating **interprovincial migration in
Canada from 1971 to 2022**, with a specific emphasis on migration
patterns on both a yearly and quarterly basis. We aim to explore whether
people prefer to migrate during specific times, the provinces that are
less favored and those that attract the most migrants, and whether
migration trends have changed over the decades. This research will
provide valuable insights about the movement of people within the
country and can become a rich resource for studying Canada's population
mobility, with applications in economics, sociology, policy development,
and urban planning.

# ABOUT DATA SET {#section-two}

This comprehensive dataset provides valuable information on the
migration patterns of individuals and families across Canada from 1971
to 2022. It specifically focuses on interprovincial migration, tracking
the movement of people between different provinces and territories. This
dataset is a crucial resource for understanding the dynamics of
population movement within Canada over several decades.

**Data Fields** - The dataset typically includes the following key data
fields:

1.  *Year:* The time period indicating the specific year in which the
    migration occurred.

2.  *Quarter:* The time period indicating the specific quarter in which
    the migration occurred.

3.  *Province or Territory of Origin:* The province or territory from
    which migrants originated. This includes data on the number of
    individuals or families moving out of each province.

4.  *Province or Territory of Destination:* The province or territory to
    which migrants are relocating. This includes data on the number of
    individuals or families moving into each province.

5.  *Number of Migrants:* The total count of individuals or families
    moving from the destination to the specified quarter.

# LOADING DATA SET

```{r}
# Reading data file 

migration_data <- read.csv("C:/Users/shiva/Documents/ADSC1910/ProjectWork/interprovincial_migration.csv",
                           header=TRUE)
head(migration_data)
```

## Displaying Column Names

```{r}
# Display variable names
cat("Variable Names:\n")
print(names(migration_data))
```

## Checking Dimensions of the dataset

```{r}
# Display dimensions of the dataset
cat("\nDimensions of the Dataset :\n")
print(dim(migration_data))
```

## Exploring Data Summary

```{r}
# Display summary statistics for numeric variables
cat("\nSummary Statistics of the Dataset :\n")
print(summary(migration_data))
```

```{r}
# We can also use the 'describe' function from the 'psych' package for a more detailed summary
library(psych)
describe(migration_data)

```

```{r}
# Display the first few rows of the dataset
print(tail(migration_data))
```

```{r, warning=FALSE}
library(tidymodels)
library(dplyr)
library(tidyr)
library(ggplot2)
library(plotly)

glimpse(migration_data)
```

```{r}
# Check for missing values in the migration_data data frame
missing_values <- sapply(migration_data, function(x) sum(is.na(x)))

# Print the number of missing values for each column
print(missing_values)
```

------------------------------------------------------------------------

# DATA PRE-PROCESSING {#section-three}

## CREATE A NEW COLUMN BASED ON "Origin" Column ; a new column will be created with the full names of the Canadian provinces and territories using a lookup table.

```{r}
# Load the dplyr package if you haven't already
#library(dplyr)

# Create a data frame with the abbreviations and full names
state_data <- data.frame(
  Origin = c("N.L.", "P.E.I.", "N.S.", "N.B.", "Que.", "Ont.", "Man.", "Sask.", "Alta.", "B.C.", "Y.T.", "N.W.T.", "Nvt."),
  ProvinceNames = c("Newfoundland and Labrador", "Prince Edward Island", "Nova Scotia", "New Brunswick", "Quebec", "Ontario", "Manitoba", "Saskatchewan", "Alberta", "British Columbia", "Yukon", "Northwest Territories", "Nunavut")
)
state_data
```

```{r}
# Use mutate to add the Full_Name column to the migration dataset
result_data <- migration_data %>%
  right_join(state_data, by = c("Origin" = "Origin"))%>%
  select(Year, Quarter, Origin, ProvinceNames, everything())
```

```{r}
result_data <- result_data %>%
  rename(
    `Newfoundland and Labrador` = "N.L.",
    `Prince Edward Island` = "P.E.I.",
    `Nova Scotia` = "N.S.",
    `New Brunswick` = "N.B.",
    `Quebec` = "Que.",
    `Ontario` = "Ont.",
    `Manitoba` = "Man.",
    `Saskatchewan` = "Sask.",
    `Alberta` = "Alta.",
    `British Columbia` = "B.C.",
    `Yukon` = "Y.T.",
    `Northwest Territories` = "N.W.T.",
    `Nunavut` = "Nvt."
  )

head(result_data, 5)
```

# TREND ANALYSIS {#section-four}

## Trends in Migration Over the years

```{r}
# Total migration over years
total_migration <- aggregate(. ~ Year, data = result_data[, -c(3:4)], FUN = sum, na.rm = TRUE)

# Plotting total migration over years
ggplotly(ggplot(total_migration, aes(x = Year, y = Total)) +
  geom_line() +
  labs(title = "Total Migration Over Years",
       x = "Year",
       y = "Total Migration"))
```

*OBSERVATIONS :* Immigrants trend across Canadian provinces doesn't
follow a patterned trend.Although, the recent years have a range of
migration count peaks (280k\~330k) that can be seen in the plot above.

# Quarterly migration trends by province

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(plotly)


# Filtering numeric columns from the original dataset
numeric_cols <- result_data %>%
  select(-c(Year, Quarter, ProvinceNames, Total)) %>%
  sapply(is.numeric)

# Extracting the names of numeric columns
numeric_col_names <- names(numeric_cols)[numeric_cols]

# Selecting the numeric columns and necessary identifier columns for melting
selected_cols <- c("Year", "Quarter", "ProvinceNames", "Total",numeric_col_names)
selected_data <- result_data[, selected_cols]

# Melting the selected numeric columns
melted_data <- selected_data %>%
  pivot_longer(cols = -c(Year, Quarter, ProvinceNames, Total), names_to = "Province", values_to = "MigrationCount")

# Plotting quarterly migration trends by province for numeric columns
plot_years <- ggplot(melted_data, aes(x = Quarter, y = MigrationCount, color = Province)) +
  geom_line(size = 1) +
  facet_wrap(~Province, scales = "free_y") +
  labs(title = "Quarterly Migration Trends Across Provinces",
       x = "Quarters",
       y = "Migration Count",
       color = "Province") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8))

# Interactive plot
interactive_plot <- ggplotly(plot_years, tooltip = c("x", "y", "color")) %>%
  layout(title = list(text = "Quarterly Migration Trends Across Provinces", size = 16),
         xaxis = list(title = "Quarters", tickfont = list(size = 10)),
         yaxis = list(title = "Migration Count", tickfont = list(size = 10)),
         legend = list(font = list(size = 8)))

interactive_plot

```

*OBSERVATIONS :* Not much of a pattern can be seen except for the fact
that majority of the provinces have high migration phase going on across
Quarter 2 & 3.

## Migration Across Candidan Province

```{r, warning=FALSE}
library(openintro)
library(ggplot2)
library(plotly)


bar_chart <-  ggplot(result_data, aes(x = ProvinceNames, y = Total, fill = ProvinceNames)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
    title = "MIGRANTS IN PROVINCE : 1971 to 2022",
    y = "MIGRANTS COUNT"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


# Get the maximum count for each province
max_counts <- result_data %>%
  group_by(ProvinceNames) %>%
  summarise(Max_Count = max(Total))

# Add maximum count labels directly to the bars
bar_chart +
  geom_text(data = max_counts, aes(label = Max_Count, y = Max_Count+205000), size = 4.5, 
            position = position_stack(vjust = 1.9), angle = 90, 
            hjust = 0.5, vjust = 0.5, 
            family = "sans") + theme(legend.position = "none")

```

## Migration Across Candidan Province Across Three Year Ranges

```{r}
# Dividing years into three equal ranges
range_1 <- result_data %>% filter(Year >= 1971 & Year <= 1991)
range_2 <- result_data %>% filter(Year >= 1992 & Year <= 2006)
range_3 <- result_data %>% filter(Year >= 2007 & Year <= 2022)

# Creating plots for each range
plot_range_1 <- ggplot(range_1, aes(x = ProvinceNames, y = Total, fill = ProvinceNames)) +
  geom_bar(stat = "identity") +
  labs(title = "1971-1991", x = "Province", y = "Count") +
  theme_minimal()+
  xlab("") + 
  theme(axis.text.x = element_blank(),  
        axis.ticks.x = element_blank()) +
  geom_text(data = range_1 %>%
  group_by(ProvinceNames) %>%
  summarise(Max_Count = max(Total)), aes(label = Max_Count, y = Max_Count+205000), size = 3.5, 
            position = position_stack(vjust = 1.9), angle = 90, 
            hjust = 0.5, vjust = 0.5, 
            family = "sans")


plot_range_2 <- ggplot(range_2, aes(x = ProvinceNames, y = Total, fill = ProvinceNames)) +
  geom_bar(stat = "identity") +
  labs(title = "1992-2006", x = "Province", y = "Count") +
  theme_minimal()+
  xlab("") + 
  theme(axis.text.x = element_blank(),  
        axis.ticks.x = element_blank()) +
  geom_text(data = range_2 %>%
  group_by(ProvinceNames) %>%
  summarise(Max_Count = max(Total)), aes(label = Max_Count, y = Max_Count+205000), size = 3.5, 
            position = position_stack(vjust = 1.9), angle = 90, 
            hjust = 0.5, vjust = 0.5, 
            family = "sans")


plot_range_3 <- ggplot(range_3, aes(x = ProvinceNames, y = Total, fill = ProvinceNames)) +
  geom_bar(stat = "identity") +
  labs(title = "2007-2022", x = "Province", y = "Count") +
  theme_minimal()+
  xlab("") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  geom_text(data = range_3 %>%
  group_by(ProvinceNames) %>%
  summarise(Max_Count = max(Total)), aes(label = Max_Count, y = Max_Count+205000), size = 3.5, 
            position = position_stack(vjust = 1.9), angle = 90, 
            hjust = 0.5, vjust = 0.5, 
            family = "sans")

```

```{r}
library(plotly)
library(patchwork)

combined_plot <- plot_range_1+ theme(legend.position = "none") + plot_range_2 + plot_range_3 + theme(legend.position = "none") +  plot_layout(ncol = 1)
combined_plot

```

*OBSERVATIONS :* "Ontario" is the province with highest migration count
and "Nunavut" have the least migration count.

## Migration Trends for Higher and Lower Migration Province Over the Quater.

```{r}
# Finding the province with the highest migration and its corresponding quarter
highest_province <- melted_data %>%
  group_by(Province) %>%
  summarise(total_migration = sum(MigrationCount)) %>%
  arrange(desc(total_migration)) %>%
  slice(1)

highest_province_name <- highest_province$Province

highest_province_quarters <- melted_data %>%
  filter(Province == highest_province_name) %>%
  group_by(Quarter) %>%
  summarise(total_migration = sum(MigrationCount)) %>%
  arrange(desc(total_migration))

highest_province_quarters$Quarter <- factor(highest_province_quarters$Quarter, levels = unique(highest_province_quarters$Quarter))

# Finding the province with the lowest migration and its corresponding quarter
lowest_province <- melted_data %>%
  group_by(Province) %>%
  summarise(total_migration = sum(MigrationCount)) %>%
  arrange(total_migration) %>%
  slice(1)

lowest_province_name <- lowest_province$Province

lowest_province_quarters <- melted_data %>%
  filter(Province == lowest_province_name) %>%
  group_by(Quarter) %>%
  summarise(total_migration = sum(MigrationCount)) %>%
  arrange(total_migration)

lowest_province_quarters$Quarter <- factor(lowest_province_quarters$Quarter, levels = unique(lowest_province_quarters$Quarter))

highest_province_quarters$proportion <- highest_province_quarters$total_migration / sum(highest_province_quarters$total_migration)

custom_colors <- c("#17becf", "#1f77b4", "#bcbd22","#9467bd", "#e377c2", "#7f7f7f")


plot_ly(data = highest_province_quarters, labels = ~Quarter, values = ~proportion, type = 'pie', marker = list(colors = custom_colors)) %>%
  layout(title = paste("Migration Trends - Highest Province:", highest_province_name),
         showlegend = TRUE)
```

*OBSERVATIONS :* Ontario have the highest trends of migrations in the
Quarter 2 & 3. This was concluded by the quarterly trends as well.

```{r}
lowest_province_quarters$proportion <- lowest_province_quarters$total_migration / sum(lowest_province_quarters$total_migration)

custom_colors <- c("#17becf", "#1f77b4", "#bcbd22","#9467bd", "#e377c2", "#7f7f7f")

# Create the pie chart with custom colors
plot_ly(data = lowest_province_quarters, labels = ~Quarter, values = ~proportion, type = 'pie', 
        marker = list(colors = custom_colors)) %>%
  layout(title = paste("Migration Trends - Lowest Province:", lowest_province_name),
         showlegend = TRUE)
```

*OBSERVATIONS :* Nunavut have the highest trends of migrations in the
Quarter 2 & 1.

------------------------------------------------------------------------

# HYPOTHESIS TESTING {#section-five}

**HYPOTHESIS 1 : People tend to migrate more frequently either yearly or
quarterly between Canadian provinces.**

*Null Hypothesis (H0):* There is no significant association between the
year/quarter and the frequency of migration between Canadian provinces.

*Alternate Hypothesis (H1):* There is a significant association between
the year/quarter and the frequency of migration between Canadian
provinces.

## To test this hypothesis, are using a Chi-Square (χ²) test

We will organize the data into a contingency table, where rows represent
one variable (e.g., year/quarter) and columns represent the other
variable (e.g., provinces), with cell values being the frequencies of
migration between provinces in each specific year/quarter.

```{r, warning=FALSE}

# Selecting the relevant columns for the contingency table
data_for_test <- result_data[, c("Year", "Quarter", "Newfoundland and Labrador", "Prince Edward Island", "Nova Scotia", "New Brunswick", "Quebec", "Ontario", "Manitoba", "Saskatchewan", "Alberta", "British Columbia", "Yukon", "Northwest Territories", "Nunavut")]

# Creating a contingency table
contingency_table <- table(data_for_test$Year, data_for_test$Quarter)

# Performing Chi-Square test
chi_square_result <- chisq.test(contingency_table)

#Test result
print(chi_square_result)
```

*OBSERVATIONS :*

1.  *Chi-squared Value:* The calculated chi-squared value is 36.932.
2.  *Degrees of Freedom (df):* The degrees of freedom are 153.
3.  *P-Value:* The obtained p-value is approximately 1.

-   Chi-squared Value Interpretation: The chi-squared value of 36.932
    indicates the magnitude of the difference between the observed and
    expected frequencies within the contingency table.

-   Degrees of Freedom: With 153 degrees of freedom, this test has
    considered a significant number of categories and observations.

-   P-Value Interpretation: The p-value of approximately 1 suggests that
    **there's insufficient evidence to reject the null hypothesis**. A
    p-value of 1 indicates very high probability under the null
    hypothesis. It implies that there is no significant association
    between the years/quarters and the migration counts among Canadian
    provinces based on the provided data.

*In summary, based on this test's results, there doesn't appear to be a
significant relationship between the timing (years/quarters) and the
migration counts among Canadian provinces.*

------------------------------------------------------------------------

**HYPOTHESIS 2 : Certain provinces consistently attract more migrants
and can be recognized as the most favorable destinations both annually
and quarterly.** **HYPOTHESIS 3 : Certain provinces consistently attract
less migrants and can be recognized as the least favorable destinations
both annually and quarterly.**

*Null Hypothesis (H0):* There is no significant difference in the
average number of migrants attracted by different provinces both
annually and quarterly.

*Alternate Hypothesis (H1):* Certain provinces consistently attract a
significantly different number of migrants, establishing themselves as
the more or less favorable destinations both annually and quarterly.

## To test this hypothesis,we are using a t-test

```{r}
library(dplyr)

# Finding provinces with the highest total migration
highest_total <- result_data %>%
  arrange(desc(Total)) %>%
  distinct(ProvinceNames, .keep_all = TRUE) %>%
  head(2) %>%
  select(ProvinceNames, Total)

# Finding provinces with the lowest total migration
lowest_total <- result_data %>%
  arrange(Total) %>%
  distinct(ProvinceNames, .keep_all = TRUE) %>%
  head(2) %>%
  select(ProvinceNames, Total)

# Extracting province names into lists
highest_province_list <- as.list(highest_total$ProvinceNames)
lowest_province_list <- as.list(lowest_total$ProvinceNames)

cat("Provinces with the highest total migration:\n")
print(highest_province_list)
cat("\nProvinces with the lowest total migration:\n")
print(lowest_province_list)

```

```{r}

# Selecting columns of provinces for comparison
provinces <- c('Ontario', 'Alberta' , 'Nunavut', 'Yukon')

# Creating an empty list to store t-test results
t_test_results <- list()

# Looping through combinations of provinces for t-tests
for (i in 1:(length(provinces) - 1)) {
  for (j in (i + 1):length(provinces)) {
    # Selecting migration data for two provinces
    province1 <- result_data[[provinces[i]]]
    province2 <- result_data[[provinces[j]]]
    
    # Performing a t-test between the two provinces
    t_test_result <- t.test(province1, province2)
    
    # Storing t-test result in the list
    comparison <- paste(provinces[i], "-", provinces[j])
    t_test_results[[comparison]] <- t_test_result
  }
}

# Printing the results of all t-tests
for (comparison in names(t_test_results)) {
  cat(comparison, ":\n")
  print(t_test_results[[comparison]])
  cat("\n")
  cat("--------------------------------------------\n")
}

```

*OBSERVATIONS :*

1.  *Ontario vs. Alberta:* There's a statistically significant
    difference in the average number of migrants attracted by Ontario
    and Alberta, with Ontario having a slightly higher average. The
    p-value of 0.04393 suggests a moderate level of confidence in
    rejecting the null hypothesis, indicating a potential difference in
    migration numbers between these provinces.

2.  *Ontario vs. Nunavut / Yukon:* Comparing Ontario with Nunavut and
    Yukon shows a substantial difference in migration numbers. e
    p-values are extremely low (p-value \< 2.2e-16), indicating an
    exceedingly high level of confidence in rejecting the null
    hypothesis. Ontario attracts significantly more migrants compared to
    Nunavut and Yukon.

3.  *Alberta vs. Nunavut / Yukon:* Similar to Ontario, Alberta attracts
    significantly more migrants compared to Nunavut and Yukon. The
    p-values are very low, indicating strong evidence against the null
    hypothesis.

4.  *Nunavut vs. Yukon:* There's a significant difference in migration
    numbers between Nunavut and Yukon. The p-value is extremely low,
    indicating a clear distinction in migration patterns between these
    territories.

**These results support the alternate hypothesis, suggesting that
certain provinces consistently attract significantly different numbers
of migrants. Ontario and Alberta emerge as leading destinations, drawing
considerably higher migration numbers compared to Nunavut and Yukon.
Additionally, Nunavut and Yukon showcase notably lower migration numbers
compared to the provinces, indicating a distinct migration pattern
between territories and provinces.**

------------------------------------------------------------------------

**HYPOTHESIS 4 : There is a changing trend in interprovincial migration
patterns over the years, reflecting evolving factors that influence
people's decisions to relocate within Canada.**

*Null Hypothesis (H0):* There is no difference in the distribution of
interprovincial migration patterns over the years.

*Alternate Hypothesis (H1):* There exists a difference in the
distribution of interprovincial migration patterns over the years.

## To test this hypothesis,we are using a Kolmogorov-Smirnov test (KS test)

```{r}
# Aggregate Migration Count by Year in each range
sum_range_1 <- aggregate(Total ~ Year, data = range_1, FUN = sum)
sum_range_2 <- aggregate(Total ~ Year, data = range_2, FUN = sum)
sum_range_3 <- aggregate(Total ~ Year, data = range_3, FUN = sum)
# Performing KS tests between aggregated migration counts
ks_test_range1_range2 <- ks.test(sum_range_1$Total, sum_range_2$Total)
ks_test_range1_range3 <- ks.test(sum_range_1$Total, sum_range_3$Total)
ks_test_range2_range3 <- ks.test(sum_range_2$Total, sum_range_3$Total)
# Printing the test results
print(ks_test_range1_range2)
cat("---------------------------------")
print(ks_test_range1_range3)
cat("---------------------------------")
print(ks_test_range2_range3)
```

*OBSERVATIONS :*

The Kolmogorov-Smirnov (KS) test results suggest interesting findings
regarding the distribution of interprovincial migration patterns across
the specified time ranges.

**Range 1 vs. Range 2:** The KS test between the migration counts of
Range 1 (1971-1991) and Range 2 (1992-2006) indicates a significant
difference in their distributions (p-value = 1.628e-05). This suggests
that there's a notable change or shift in migration patterns between
these time periods.

**Range 1 vs. Range 3:** The KS test between the migration counts of
Range 1 (1971-1991) and Range 3 (2007-2022) also reveals a significant
difference in their distributions (p-value = 0.002707). This further
emphasizes a substantial shift or alteration in migration trends over
time.

**Range 2 vs. Range 3:** However, the KS test between the migration
counts of Range 2 (1992-2006) and Range 3 (2007-2022) does not show a
significant difference (p-value = 0.1879). This suggests that the
migration patterns between these periods might be relatively similar.

-   Given these results, the evidence supports rejecting the null
    hypothesis for comparisons between Range 1 vs. Range 2 and Range 1
    vs. Range 3. This implies that there are notable differences in
    migration distributions between these time frames.

-   However, for Range 2 vs. Range 3, the p-value is not significant,
    suggesting that the distributions might not differ significantly
    between these periods.

Thus, there is support for the alternative hypothesis (H1) that
indicates differences in migration distributions between certain
periods, signifying changing trends in interprovincial migration
patterns over the years.

------------------------------------------------------------------------

# CONCLUSION {#section-six}

The project on analyzing changing interprovincial migration trends in
Canada from 1971 to 2022 has yielded valuable insights through various
statistical tests, shedding light on different aspects of migration
patterns within the country.

**Chi-Square Test:**

The Chi-Square test outcomes suggest that there isn't a significant
relationship between the timing (years/quarters) and migration counts
among Canadian provinces. This implies that migration trends might not
be notably influenced by specific temporal patterns on a yearly or
quarterly basis.

**T-Test Findings:**

The T-test results strongly support the alternate hypothesis,
highlighting that specific provinces consistently attract significantly
higher numbers of migrants. Ontario and Alberta emerge as primary
destinations, drawing notably higher migration figures compared to
Nunavut and Yukon. This emphasizes distinct migration patterns between
territories and provinces, with the latter attracting considerably more
migrants.

**KS Test Insights:**

The Kolmogorov-Smirnov (KS) test results provide evidence supporting the
idea of changing trends in interprovincial migration patterns over time.
Notably, there are significant differences in migration distributions
between certain periods, indicating evolving migration trends across the
years studied.

In conclusion, these comprehensive statistical analyses offer nuanced
insights into Canada's interprovincial migration dynamics. They uncover
the influence of specific provinces in attracting migrants, highlight
the absence of clear temporal migration patterns, and confirm the
presence of changing trends in migration distributions over the studied
decades. This research contributes significantly to understanding
population mobility within Canada, with implications across diverse
fields such as economics, sociology, policy development, and urban
planning.

------------------------------------------------------------------------

# REFERNCES {#section-seven}

1.  DATASET Source : Estimates of interprovincial migrants by province
    or territory of origin and destination, quarterly and yearly in
    Canada from 1971 to 2022.
    (<https://catalogue.data.gov.bc.ca/dataset/inter-provincial-and-international-migration/resource/f6171cc3-3845-40dd-9855-d87e8f524064/>)

2.  ADSC1910_01 - Applied Data Science/ Lecture Notes

3.  Hypothesis Testing :
    <https://www.r-bloggers.com/2022/12/hypothesis-testing-in-r/>

4.  Interactive Plots in R :
    <https://r-graph-gallery.com/interactive-charts.html>
